### 2024-01-07 doc/Thesis/chapter/01-introduction.tex
first correction round

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Photovoltaics (PV) is one viable option for becoming carbon neutral. 
Furthermore, 
it uses the sun's energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search} which harness the whole power output of the sun.
%
One sort of PV are CIGS (copper indium gallium sulfide) cells\cite{Vasekar2010}. 
Due to their large absorption coefficient (compared to silicon based cells), less material is needed and they can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple cells are operated in series. 
The cells must be applied to a non-conducting surface.
Glass is a popular non-conducting substrate, but very rigid and brittle. 
An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be synthesised on top.
Polymers would be a obvious choice if not for its low thermal stability which makes high production temperatures impractical.
A non-toxic material which is suitable for the insulation is \ch{ZrO2}. 
%An economic and scalable method is doctor blading via a sol-gel process. 
Sol-gel roll-to-roll coating processes (e.g. tape casting) are economic and scalable methods to apply liquid precursors to substrates.
Sol-gel processes often produce porous layers, though. 
In this work a dense, insulating and homogeneous layer is pursued. 
Machine learning can help to uncover complex non-linear relations, such as the 
dependence of the thickness and resistance of the resulting layer on production factors.
%\td{influence} of the production factors on the thickness and resistance of the resulting layer.
The minimization of the conductance of the layer is performed with a particle swarm optimization 
algorithm. 
%The resulting optimum is compared with other optimization methods.
\td{and how do you transfer knowledge ...}

@@

The remainder of this work is organized with chapter 
\ref{sec:theoretical} giving 
%some background information on topics of PV, \td{material science} and \td{computational science (more detail)} which were used in this work. 
information on the general \td{functionsweise} of PV, the structure, characteristics and properties of materials which were used and computational, statistical and machine learning methods for data processing.

>>>>

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Photovoltaics (PV) is one viable option for becoming carbon neutral. 
Furthermore, 
it uses the sun's energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search} which harness the whole power output of the sun.
%
One sort of PV are CIGS (copper indium gallium sulfide) cells\cite{Vasekar2010}. 
Due to their large absorption coefficient (compared to silicon based cells), less material is needed and they can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple cells are operated in series. 
The cells must be applied to a non-conducting surface.
Glass is a popular non-conducting substrate, but very rigid and brittle. 
An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be synthesised on top.
Polymers would be a obvious choice if not for its low thermal stability which makes high production temperatures impractical.
A non-toxic material which is suitable for the insulation is \ch{ZrO2}. 
%An economic and scalable method is doctor blading via a sol-gel process. 
Sol-gel roll-to-roll coating processes (e.g. tape casting) are economic and scalable methods to apply liquid precursors to substrates.
Sol-gel processes often produce porous layers, though. 
In this work a dense, insulating and homogeneous layer is pursued. 
Machine learning can help to uncover complex non-linear relations, such as the 
dependence of the thickness and resistance of the resulting layer on production factors.
%\td{influence} of the production factors on the thickness and resistance of the resulting layer.
The minimization of the conductance of the layer is performed with a particle swarm optimization 
algorithm which has the coating process variables as input. 
%The resulting optimum is compared with other optimization methods.
%\td{and how do you transfer knowledge ...}

@@

The remainder of this work is organized with chapter 
\ref{sec:theoretical} giving 
%some background information on topics of PV, \td{material science} and \td{computational science (more detail)} which were used in this work. 
information on the general working principles of PV, the structure, characteristics and properties of materials which were used and computational, statistical and machine learning methods for data processing.

### 2024-01-07 doc/Thesis/chapter/020-theory-materials.tex
first correction round

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{History of Photovoltaics}
The photoelectric effect was first described in 1839 by french scientist Alexandre 
Edmond \linebreak[4] 
Becquerel\cite{becquerel1839memoire}. %, the father of Henri Becquerel (the person after whom the unit is named).
Another relevant piece in the \gls{pv} jigsaw was brought to light
%discovered
with the discovery of photo conductivity of selenium
by British engineer Willouhgby Smith\cite{Smith1873Selenium}.
In 1876 William Adams and Richard Day\cite{Adams1876Selenium} showed that 
the energy of light can be directly converted into electrical energy by a bar of 
selenium with attached platinum electrodes.
And finally, in 1905 Einstein described the physical background of the photoelectric 
effect with his light quantum theory\cite{einstein1905erzeugung}.
%\todo{https://doi.org/10.1063/1.1716492}
In the late 1950s the first solar cells (with efficiencies under 10 percent) were used in niche applications such as space exploration.  
In 1958 the US American Vanguard I\cite{vanguard2004} and the soviet Sputnik III\cite{sputnik} were the first satellites with solar cells with efficiencies under 10 \% (\td{cite?}).
These "solar batteries" - as they were called then - allowed the transmission system of Vanguard I to be operating for over a year after the chemical battery powered system stopped transmitting after 20 days\cite{vanguard2004}. 
%
Eventually, the interest in photovoltaic and other alternative energy sources 
rose - fuelled by the oil crisis in 1973 - 
and the development of photovoltaic devices for the consumer market was boosted. 
This development lead to a drop in 
average price for \gls{pv} module from \$ 100 per watt in 1975 to \$ 4 per watt in 2007\cite{pagliaro2008flexible}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{History of Photovoltaics}
The photoelectric effect was first described in 1839 by french scientist Alexandre 
Edmond \linebreak[4] 
Becquerel\cite{becquerel1839memoire}. %, the father of Henri Becquerel (the person after whom the unit is named).
Another relevant piece in the \gls{pv} jigsaw was brought to light
%discovered
with the discovery of photo conductivity of selenium
by British engineer Willouhgby Smith\cite{Smith1873Selenium}.
In 1876 William Adams and Richard Day\cite{Adams1876Selenium} showed that 
the energy of light can be directly converted into electrical energy by a bar of 
selenium with attached platinum electrodes.
And finally, in 1905 Einstein described the physical background of the photoelectric 
effect with his light quantum theory\cite{einstein1905erzeugung}.
%\todo{https://doi.org/10.1063/1.1716492}
In the late 1950s the first solar cells (with efficiencies under 10 percent) were used in niche applications such as space exploration.  
In 1958 the US American Vanguard I\cite{vanguard2004} and the soviet Sputnik III\cite{sputnik1959} were the first satellites with solar cells with efficiencies under 10 \% (\td{cite?}).
These "solar batteries" - as they were called then - allowed the transmission system of Vanguard I to be operating for over a year after the chemical battery powered system stopped transmitting after 20 days\cite{vanguard2004}. 
%
Eventually, the interest in photovoltaic and other alternative energy sources 
rose - fuelled by the oil crisis in 1973 - 
and the development of photovoltaic devices for the consumer market was boosted. 
This development lead to a drop in 
average price for \gls{pv} module from \$ 100 per watt in 1975 to \$ 4 per watt in 2007\cite{pagliaro2008flexible}.

### 2024-01-07 doc/Thesis/chapter/021-theory-calculations.tex
first correction round

A \gls{ga} is a search algorithm that uses principles of natural selection and \td{genetics} to optimize a search space. A GA starts with a population of randomly generated solutions, or chromosomes, and then proceeds to breed them together to create new solutions. The new solutions are then tested for fitness, and the best solutions are selected to create the next generation of chromosomes. This process is repeated until a \td{satisfactory} solution is found.\footnote{This paragraph was written by GPT3\cite{Liu2021gpt} given the input "Introduction to genetic algorithms: "}

>>>>

A \gls{ga} is a search algorithm that uses principles of natural selection and genetics (mutations and recombination) to optimize a search space. A GA starts with a population of randomly generated solutions, or chromosomes, and then proceeds to breed them together to create new solutions. The new solutions are then tested for fitness, and the best solutions are selected to create the next generation of chromosomes. This process is repeated until a \td{satisfactory} solution is found.\footnote{This paragraph was written by GPT3\cite{Liu2021gpt} given the input "Introduction to genetic algorithms:"}
